Ordinal bhsdtr tutorial

### 2020-02-18 ordinal/Readme.Rmd
a remark about additive item and person effects

Unfortunately, without additional assumptions, it is impossible to
model both kinds of variability at the same time even in the
hypothetical repeated-measurement-with-memory-wipeout-scenario,
because every shift in the internal value is indistinguishable from a
uniform effect in the thresholds, i.e., a constant shift of all the
thresholds. As I hope you already realize, the required additional
assumptions that make such models identifiable under certain
conditions are necessarily causal.

>>>>

Unfortunately, without additional assumptions (e.g., additivity of
item and participant effects), it is impossible to model both kinds of
variability at the same time even in the hypothetical
repeated-measurement-with-memory-wipeout-scenario, because every shift
in the internal value is indistinguishable from a uniform effect in
the thresholds, i.e., a constant shift of all the thresholds. As I
hope you already realize, the required additional assumptions that
make such models identifiable under certain conditions are necessarily
causal.
